---
title: "Description of the playWithR package"
author: "Isabelle Valette"
date: "2017-01-21"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Description of the package}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---
## Overview of the package functions

The functions included in this packages are:

|Function           |Description                                                  |
|:------------------------|:------------------------------------------------|
|`fars_read()`            |Read csv files                                   |
|`make_filename()`        |Make a file name                           |
|`fars_read_years()`      |Load MONTH and year into R    |
|`fars_summarize_years()` |Count the number of accidents per month and year                     |
|`fars_map_state()`       |Plot the location of accidents on US maps    |

## Data Source
The functions contained in this package are created for manipulating data from  the US National Highway Traffic Safety Administration's Fatality Analysis Reporting System, which is a nationwide census providing the American public yearly data regarding fatal injuries suffered in motor vehicle traffic crashes.

Data can be found [here](https://www.coursera.org/learn/r-packages/peer/25XGp/documenting-code)

## Reading csv files
This function loads a csv file in R and converts it to a data frame tbl
Here is an example on how to use this function:

```{r, example1, eval = FALSE}
dt <- fars_read("accident_2013.csv.bz2")
```

## Make a file name
This function combines text with an input value to create a file name for the data from the US National Highway Traffic Safety Administration's Fatality Analysis Reporting System.
```{r, example2, eval = FALSE}
#Include a list of years
make_filename(list(2013, 2014, 2015))
#Include only a subset of numerical value
make_filename(2014:2015)
```

## Load MONTH and year 
This function reads yearly and monthly data from the US National Highway Traffic Safety Administration's Fatality Analysis Reporting System and returns an error if the selected years are not written corrected, found in the working directory files or if the working directory is not set properly.
```{r, example3, eval = FALSE}
l <- fars_read_years(2013)
```

##Count the number of accidents per month and year
This function load data from data from the US National Highway Traffic Safety Administration's Fatality Analysis Reporting System, binds the yearly data together, group by year and month, counts th number of accidents and spread the results with month in rows and a year per column.

```{r, example4, eval = FALSE}
head(fars_summarize_years(2013:2015))
```

## Plot the location of accidents on US maps
This function load accident data from the US National Highway Traffic Safety Administration's Fatality Analysis Reporting System, into R for a specified year and state numbers, validate the parameters and plot the location of accidents on a US map.
```{r, example5, eval = FALSE}
fars_map_state(c(1:56),2014)
```

## References
Peer Assignment in Coursera Course "Building R Packages". 