---
title: "Description of the faRs package"
author: "Isabelle Valette"
date: "2017-01-21"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Description of the package}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---
## Overview of the package functions

The functions included in this packages are:

|Function           |Description                                                  |
|:------------------------|:------------------------------------------------|
|`fars_read()`            |Read csv files                                   |
|`make_filename()`        |Make a file name                           |

## Data Source
The functions contained in this package are created for manipulating data from  the US National Highway Traffic Safety Administration's Fatality Analysis Reporting System, which is a nationwide census providing the American public yearly data regarding fatal injuries suffered in motor vehicle traffic crashes.

Data can be found [here](https://www.coursera.org/learn/r-packages/peer/25XGp/documenting-code)

## Reading csv files
This function loads a csv file in R and converts it to a data frame tbl
Here is an example on how to use this function:

```{r, example1, eval = FALSE}
dt <- fars_read("accident_2013.csv.bz2")
```

## Make a file name
This function combines text with an input value to create a file name for the data from the US National Highway Traffic Safety Administration's Fatality Analysis Reporting System.
```{r, example2, eval = FALSE}
#Include a list of years
make_filename(list(2013, 2014, 2015))
#Include only a subset of numerical value
make_filename(2014:2015)
```

## References
Peer Assignment in Coursera Course "Building R Packages". 